Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-08-12 GWLDCI.tex
paper 1 abstract minor tweaks

\begin{abstract}
  Wilson loop diagrams, an important tool in studying scattering amplitudes of SYM $N=4$ theory, are known by previous work to be associated to positroids. We characterize when two Wilson loop diagrams give the same positroid, prove that an important subclass of subdiagrms (exact subdiagrams) correspond to uniform matroids and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.  We also give a correspondence between those positroids which can arise from Wilson loop diagrams and directions in associahedra.
\end{abstract}

>>>>

\begin{abstract}
  Wilson loop diagrams are an important tool in studying scattering amplitudes of SYM $N=4$ theory and are known by previous work to be associated to positroids. We characterize the conditions under which two Wilson loop diagrams give the same positroid, prove that an important subclass of subdiagrams (exact subdiagrams) correspond to uniform matroids, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.  We also give a correspondence between those positroids which can arise from Wilson loop diagrams and directions in associahedra.
\end{abstract}
